---
title: "Covid Unemployment Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

## Introduction


We are interested in “Unemployment during the Covid pandemic” because we want 
to find out how it the pandemic has contributed to unemployment and if there 
are certain groups of people who are more unemployed than others during the 
pandemic.


## Summary 
Write a summary paragraph that includes information calculated by your summary 
information function


## Table 

```{r setup, include=FALSE}
kable(job_gains_or_loss_by_race)
```

For the Covid Unemployment data, we renamed some columns for better
readibility and calculated the summary of the total change in the number of
job gains or loss by each four race, that being African-American, Hispanic, 
Other, and White. We thought that this might give us an insight as to
which racial communities are most impacted and have lost the most jobs due to
the the pandemic.
We found that each of the four experienced loss of job during the 
pandemic, with the highest total change .... [editing]


```{r setup, include=FALSE}
kable(cumulative_cases_by_race)
```

For the Covid By Race data, decided to calculate the total cases of covid
by each racial group to further determine which racial groups have been 
most impacted by covid. Based on the table, multiracial groups, 
Native Americans/Alaska Natives, and Native Hawaiian/Pacific Islanders
consistently tested the least positive for covid-19. After May 31, 2020 in 
WA state, Hispanics, Blacks, and Unknown races consistently tested more 
positive than Whites until October 14, where Whites and Unknown races
test more positive than Hispanics and Blacks.


```{r setup, include=FALSE}
kable(rate_increase_in_cases_by_race)
```


For the Covid By Race data, decided to calculate the rate of increase of new 
covid cases by each racial group to further determine which racial groups 
have been most impacted by covid. We found that on May 3, the rate
of increase in new covid cases was 480.3 among Native Hawaiian/Pacific
Islanders. In addition, frican Americans also have the greatest rate of 
increase of new covid cases over time during the pandemic.



## Chart 1
Describe the purpose of each chart (e.g., "this chart was intended to show the 
relationship between..."), render each chart, and describe pertinent 
observations found in each chart


## Chart 2
Describe the purpose of each chart (e.g., "this chart was intended to show the 
relationship between..."), render each chart, and describe pertinent 
observations found in each chart


## Chart 3
Describe the purpose of each chart (e.g., "this chart was intended to show the 
relationship between..."), render each chart, and describe pertinent 
observations found in each chart

