---
title: "Covid Unemployment Project"
author: Lynn Chou, Tammy Hu, Anna Shi, Jonathan Que Trinh
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(tidyverse)
source("chart1.R")
source("chart2.R")
source("chart3.R")
source("table.R")
source("intro_summary.R")
knitr::kable(rate_increase_in_cases_by_race, format = "markdown")
```



## Introduction
We are interested in “Unemployment during the Covid pandemic” because we want
to find out how it the pandemic has contributed to unemployment and if there
are certain groups of people who are more unemployed than others during the
pandemic.



## Summary
The world has been greatly impacted by the Coronavirus. The US experienced the
most cases and deaths in the entire world. The state with the most deaths is
`r summary_info$state_with_the_most_deaths`. Coincidentally, the state that experienced the
most Black deaths is also `r summary_info$state_with_the_most_black_deaths`. In the US, minority
communities experienced highest rates of death. On a daily average, the minority
community experiences `r summary_info$minority_average_death_count` deaths. The Black community
have especially been impacted by the pandemic. Their community experiences a average daily
death count of `r summary_info$african_average_death_count`. Minority groups make up
`r summary_info$percentage_of_minority_deaths`% of deaths in the US, with the Black community making up
`r summary_info$percentage_of_black_deaths`% of the minority death population. In general, minority groups
have been the most vulnerable during the pandemic, being more exposed to the virus and experience
deaths at higher rates than white communities.



```{r echo = F, message = FALSE}
kable(job_gains_or_loss_by_race)
```

For the COVID Unemployment data, we renamed some columns for better
readability and calculated the summary of the total change in the number of
job gains or loss by each four race, that being African-American, Hispanic,
Other, and White. We thought that this might give us an insight as to
which racial communities are most impacted and have lost the most jobs due to
the the pandemic.
We found that each of the four experienced loss of job during the
pandemic, with the race with the highest impact is White, but proportionally
to their populations, Hispanic and African-Americans are more impacted by the
loss of unemployment during the pandemic.


## White with COVID outside of total white population 

```{r echo = F, comment="", prompt= FALSE, null_prefix=TRUE}
white_covid_ratio
```

## African-Americans with COVID out of the total African American population 

```{r echo = F, comment="", prompt = FALSE}
Black_covid_ratio 
```


## Hispanics with COVID out of the total Hispanics population 

```{r echo = F, comment = "", prompt = FALSE}
Hispanics_covid_ratio
```


## Aggregate Table Script: Cumulative Cases by Race 
```{r echo = F}
kable(cumulative_cases_by_race)
```




For the Covid By Race data, decided to calculate the total cases of covid
by each racial group to further determine which racial groups have been
most impacted by covid. Based on the table, multiracial groups,
Native Americans/Alaska Natives, and Native Hawaiian/Pacific Islanders
consistently tested the least positive for covid-19. After May 31, 2020 in
WA state, Hispanics, Blacks, and Unknown races consistently tested more
positive than Whites until October 14, where Whites and Unknown races
test more positive than Hispanics and Blacks.


## Aggregate Table Script: Rate of Increase in cases by Race
```{r echo = F}
kable(rate_increase_in_cases_by_race)
```

For the Covid By Race data, decided to calculate the rate of increase of new
covid cases by each racial group to further determine which racial groups
have been most impacted by covid. We found that on May 3, the rate
of increase in new covid cases was 480.3 among Native Hawaiian/Pacific
Islanders. In addition, African Americans also have the greatest rate of
increase of new covid cases over time during the pandemic.


## Chart 1
```{r echo = F}
unemployment_by_race
```

This chart was intended to show the relationship between race and percentage
unemployed. Based on the observed data, unemployment percentages are relatively
similar between races, however, white unemployment rate appear higher than
African-American, Hispanic, and other races.


## Chart 2
```{r echo = F}
employment_by_month
```

This chart was intended to show the trends of employed individuals across a
year by month. The observed data shows a significant dip during months march
through may, slowly rising in numbers going into fall season.



## Chart 3
```{r, echo = F, warning=FALSE}
employment_range
```

This chart was intended to show the relationship between fluctuation of
employment between EA-19 and G-7 between Nov 2019 to January 2021.
The observed data shows that while countries like Japan (JPN), Korea (KOR),
and Russia (RUS) did not go through much fluctuations of employment in the
given timer period, countries such as Canada (CAN), Chile (CHL), Columbia (COL),
 and USA went through mroe employment rate fluctuations.
